---
title: "Evaluative Conditioning without awareness: Replicable effects do not equate replicable inferences"
subtitle: "Analyses"
author: "Ian Hussey^[Ghent University. Email: ian.hussey@ugent.be]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    number_sections: no
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE)

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999) 

```

# Data, dependencies & functions

```{r}

# Dependencies ----

check_for_and_install_packages <- function(package) {
  if (!package %in% installed.packages()) install.packages(package)
}

check_for_and_install_packages("tidyverse")
check_for_and_install_packages("metafor")
check_for_and_install_packages("knitr")
check_for_and_install_packages("kableExtra")
check_for_and_install_packages("BayesFactor")
check_for_and_install_packages("broom")
if (!"patchwork" %in% installed.packages()) devtools::install_github("thomasp85/patchwork")

library(tidyverse)
library(metafor)
library(knitr)
library(kableExtra)
library(BayesFactor)
library(broom)
library(patchwork)

# data ----

# # read data from the main project's folder
# data_from_rrr <- read.csv("../../unconscious-ec-RRR/data/processed/data_processed.csv")
# # write to disk for this project
# write_csv(data_from_rrr, "../data/data_from_rrr.csv")

data_processed <- read.csv("../data/data_from_rrr.csv") %>%
  mutate(data_collection_site = dplyr::recode(data_collection_site,
                                              "Balas and Sarzynnska" = "Balas",
                                              "Corneille and Mierop" = "Mierop",
                                              "Gast Richter and Benedict" = "Gast",
                                              "Gawronski" = "Gawronski",
                                              "Hutter" = "Hütter",
                                              "Kurdi and Ferguson" = "Kurdi",
                                              "Moran Hussey and Hughes" = "Moran",
                                              "Olsen and Fritzlen" = "Olson",
                                              "Smith and Douglas" = "Douglas",
                                              "Stahl Bading Aust Heycke and Thomasius" = "Stahl",
                                              "Unkelbach and Hogden" = "Unkelbach",
                                              "Vadillo" = "Vadillo"),
         data_collection_site = fct_relevel(data_collection_site,
                                            "Balas",
                                            "Douglas",
                                            "Gast",
                                            "Gawronski",
                                            "Hütter",
                                            "Kurdi",
                                            "Mierop",
                                            "Moran",
                                            "Olson",
                                            "Stahl",
                                            "Unkelbach",
                                            "Vadillo")) %>%
  filter(exclude_surveillance == FALSE & 
           simulated_data == FALSE) %>%
  mutate(exclude_all_four_combined = ifelse(exclude_aware_olsen_and_fazio +
                                              exclude_aware_olsen_and_fazio_modified +
                                              exclude_awareness_baranan_dehouwer_nosek +
                                              exclude_awareness_baranan_dehouwer_nosek_modified > 0, 1, 0)) %>%
  rename(DV = sum_score_evaluation_CSpos_preferred) %>%
  mutate(DV_uninverted = ifelse(condition == "CS1_USneg", DV*-1,
                                ifelse(condition == "CS1_USpos", DV, NA))) %>%
  dplyr::select(data_collection_site,
                DV,
                DV_uninverted,
                condition,
                exclude_aware_olsen_and_fazio,
                exclude_aware_olsen_and_fazio_modified,
                exclude_awareness_baranan_dehouwer_nosek,
                exclude_awareness_baranan_dehouwer_nosek_modified,
                exclude_all_four_combined) 

data_combined_criteria <- data_processed %>%
  filter(exclude_all_four_combined == FALSE)


# Define functions ----



# add heterogeneity metrics to metafor forest plot
add_heterogeneity_metrics_to_forest <- function(fit) {
  bquote(paste("RE Model (", 
               italic('I')^"2", " = ", .(formatC(format(round(fit$I2, 1), nsmall = 1))),
               "%, ", italic('H')^"2", " = ", .(formatC(format(round(fit$H2, 1), nsmall = 1))), ")"))
}

# function to round all numerics in a data frame
round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))
  df[,nums] <- round(df[,nums], digits = digits)
  (df)
}

# apa format p value
apa_p_value <- function(p){
  p_formatted <- ifelse(p >= 0.001, paste("=", round(p, 3)),
                        ifelse(p < 0.001, "< .001", NA))
  p_formatted <- gsub(pattern = "0.", replacement = ".", x = p_formatted, fixed = TRUE)
  p_formatted
}

```

# New meta analysis: EC effect using compound exclusion criterion

We provide a more severe test of the verbal hypothesis: participants are scored as aware if *any* of the four criteria flag them as aware and excluded from the meta analysis.

```{r}

n_participants <- data_combined_criteria %>%
  dplyr::select(DV, data_collection_site) %>%
  count() %>%
  pull(n)

k_sites <- data_combined_criteria %>%
  distinct(data_collection_site) %>%
  count() %>%
  pull(n)

```

N after combined exclusions = `r n_participants`, k sites = `r k_sites`.

## Bayes factor meta-analysis

Using Rouder and Morey (2011) method: First calculate t values for each site, then use the "meta.ttestBF" function to calculate a meta analysis BF.

Following a reviewer suggestion, we have included a BF meta analysis with a scaling factor of 0.2/7 on the basis that "As the uncorrected meta-analysis gave an effect of 0.2, 0.2 is a maximum. The rough maximum for a Cauchy is 7 scale factors out (in the sense that 5% of the area is beyond this). So an appropriate scale factor would be 0.2/7."

```{r}

results_ttests <- data_combined_criteria %>% 
  dplyr::select(data_collection_site, DV) %>%
  group_by(data_collection_site) %>%
  do(ttest = tidy(t.test(.$DV))) %>%
  unnest(ttest) %>%
  rename(t = statistic, 
         df = parameter) %>%
  mutate(n = df + 1)

meta_bf <-
  meta.ttestBF(t = results_ttests$t,
             n1 = results_ttests$n,
             rscale = 0.2/7)

meta_bf_samples <-
  meta.ttestBF(t = results_ttests$t,
               n1 = results_ttests$n,
               rscale = 0.2/7,
               posterior = TRUE,
               iterations = 10000)

bf10 <- data.frame(key = "BF10", value = extractBF(meta_bf)$bf)

meta_bf_samples %>%
  as.data.frame() %>%
  dplyr::summarize(delta_estimate = quantile(delta, 0.500),
                   hdi_lower      = quantile(delta, 0.025),
                   hdi_upper      = quantile(delta, 0.975)) %>%
  gather() %>%
  bind_rows(bf10) %>%
  round_df(2) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

